---
title: "Hunters_to_harvests"
author: "Wendel Raymond"
date: "August 19, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Code for Ecosphere "Location specific factors influence patterns and effects of subsistence sea otter harvest in Southeast Alaska"
Wendel W. Raymond, M. Tim Tinker, Michelle L. Kissling, Brad Benter, Verena A. Gill, Ginny L. Eckert
wraymond2@alaska.edu

# Hunters to harvests
The goal is to assign unique hunter IDs to specific hunts to that the number of hunters hunting in a subregion can be calculated. This would be an improvment over assuming that the village were the the harvest was reported was directly adjecent to where the sea otter came from.

```{r libraries}
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(BMS)
library(sp)
library(rgdal)

theme_set(theme_classic())
```

## Data
Harvest and hunter data can be obtained from USFWS Marking Tagging and Reporting Program.
```{r data}
# Harvest #
harv <- read.csv()

# Hunter harvest data #
hunt <- read.csv()
hunt$Hunter_Name <- as.character(hunt$Hunter_Name)
```

## Prep for merging
To merge, date and location need to be in the same fromat.
```{r prep}
str(hunt)
str(harv)
```

## Merge
```{r merge}
dat <- merge(harv, hunt[, c(1:5)], by.x = c("Kill.Loc", "Year", "Tag.Loc.Name"), by.y = c("Kill_Location", "Year", "Village"), all.x = TRUE)
```

