---
title: "Least_cost_distance_subpopulations"
author: "Wendel Raymond"
date: "August 19, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---
# Code for Ecosphere "Location specific factors influence patterns and effects of subsistence sea otter harvest in Southeast Alaska"
Wendel W. Raymond, M. Tim Tinker, Michelle L. Kissling, Brad Benter, Verena A. Gill, Ginny L. Eckert
wraymond2@alaska.edu

# Least cost distance of Subpopulations
The distance from one subpopulation centroid to all other subpopulations centroids will be calculated. This will be done using a cost distance caluclation in order to restrict path movements to water bodies that sea otter are likley to travel in. 

```{r libraries}
library(dplyr)
library(ggplot2)
library(spatstat)
library(maptools)
library(rgdal)
library(rgeos)
library(raster)
library(gdistance)
library(matrixStats)
```

## Data
For analysis we will need the shapefile of subpopulation centoids and a cost raster. 
```{r data}
## Centroids ##
# Run this code in this order! This will extract the names bofore you delete them #
centroids <- readOGR(dsn="All_data", layer="SEAK_Subpopulations_Centroids_WR_UTM")

## Cost Raster with 250 meter grid cells ##
cost.rast <- raster("All_data/seakrast_250m.tif")
```

Now for some data clean up and preparation. We need to remove the Yakutat subpopulation because we assume that there is not movement in or out of the subpopulation.
```{r data prep}
# Append coordinants #
centroids <- cbind(centroids@data, centroids@coords)

# Remove Yakutat #
centroids <- centroids[!(centroids$Subpop == "YAK"),]

# Save names #
names <- as.character(centroids$Subpop)

# Covert to just coordinants #
centroids <- data.frame(cbind(centroids$coords.x1, centroids$coords.x2))

# Convert to SpatialPoints #
centroids <- SpatialPoints(centroids)
```

Check data
```{r plot data check}
plot(centroids)

plot(cost.rast)
```

## Calculate Distance
Calculate the distance from all centroids to all other centroids by restricting path to the cost raster.
```{r dist calc}
## Create Tansition layer ##
trans.lyr <- transition(1/cost.rast, transitionFunction = mean, directions = 8)
trans.lyr <- geoCorrection(trans.lyr, type = "c")

## Actual Calculation ##
centroids.dist <- costDistance(x = trans.lyr, centroids, centroids)

## Clean up data frame ##
centroids.dist <- data.frame(centroids.dist)
centroids.dist <- cbind(names, centroids.dist)
colnames(centroids.dist) <- c("Subpop", names)
```

## Export
```{r export}
## Write Table ##
write.csv(centroids.dist, file = "All_Data/Centroids_LCD.csv", row.names = names)

## Write Transition Layer ##
writeRaster(trans.lyr, file = "LCD Raster Trans.tif", format = "GTiff")
```

## Calculate mean distance
```{r summary dist}
Centroids_LCD <- read.csv("All_Data/Centroids_LCD.csv")

Bmat <- as.matrix(Centroids_LCD[,3:ncol(Centroids_LCD)])

nrdist <- numeric()

for(i in 1:nrow(Bmat)){
  nrdist[i] = min(Bmat[which(Bmat[,i] > 0),i])
}

hist(nrdist, 25)
mean_neighbour_dist_km <- mean(nrdist/1000)
sd_neighbour_dist_km <- sd(nrdist/1000)
```

